Let's Play Congestion Control

### 2017-10-10 tex/paper.tex
Tuned constants

  \begin{scope}
    \node [place,tokens=1] (s1) at (\nd{1}, \nd{3}) [label=Received feedback] {};
    \node [place] (s2) at (\nd{1}, \nd{2}) [label={[align=center]left:Received\\ACKs}] {};
    \node [place] (s3) at (\nd{3}, \nd{2}) [label={[align=center]above:Packets\\in the\\network}] {};
    \node [place,tokens=1] (s4) at (\nd{1}, \nd{0}) [label={[align=center]below:Open\\congestion\\window\\(cwnd)}] {};

>>>>

  \begin{scope}
    \node [place,tokens=1] (s1) at (\nd{0}, \nd{1}) [label=Received feedback] {};
    \node [place] (s2) at (\nd{1}, \nd{2}) [label={[align=center]left:Received\\ACKs}] {};
    \node [place] (s3) at (\nd{2}, \nd{1}) [label={[align=center]above:Packets\\in the\\network}] {};
    \node [place,tokens=1] (s4) at (\nd{1}, \nd{0}) [label={[align=center]below:Open\\congestion\\window\\(cwnd)}] {};
